Kyoto VR MQP Paper First Draft

### 2019-09-03 paper.tex
challenges of AR development section

As smartphones and mobile technology becomes more prevalent,
new forms of human-computer interaction are becoming mainstream. Smartphones
allow for an unprecedented degree of connectivity with the digital world, but
can also serve as a tool for enhancing the physical world. In this section we
explain the origins and uses of some of this technology.

@@

Augmented Reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from Virtual Reality (VR), in that a VR experience consists
exclusively of virtual information. In AR, virtual information is mixed with
sensory input from the real world~\autocite{carmigniani2011}. This can enhance
the user's perception of reality by providing information that would be
difficult or impossible to display through traditional means.

@@

>>>>

As smartphones and mobile technology become more prevalent,
new forms of human-computer interaction are becoming mainstream. Smartphones
allow for an unprecedented degree of connectivity with the digital world, but
can also serve as a tool for enhancing the physical world. In this section we
explain the origins and uses of some of this technology.

@@

Augmented Reality, or AR, is a type of human-computer interface where
perceptions of the real world are enhanced by computer-generated information.
This differs from Virtual Reality (VR) in that a VR experience consists
exclusively of virtual information. In AR, virtual information is mixed with
sensory input from the real world~\autocite{carmigniani2011}. This can enhance
the user's perception of reality by providing information that would be
difficult or impossible to display through traditional means.

@@

As we have said, AR is a new and growing field full of opportunities. But of course,
as with anything new, our understanding of AR and how to develop for it is limited.
And with those limitations come challenges. All sorts of different challenges and
limitations face the development and production of AR apps. Here are some that
we considered when working on our app.

Many of the applications and use cases that exist for AR right now are, simply put,
not very good. This means a few different things. For starters, many AR apps and
features available on smartphones offer very little in the way of functionality or
practicality; quite simply, they are primarily used for minor spectacles and simple
tricks~\autocite{theappsolutions2018}. For example, one of the most popular apps
to use AR, Pokemon GO, primarily uses it's AR feature to place a Pokemon in the
world aroudn you through your phone camera for you to capture. But when it is in
the world, it does not interact with anything around it. It just floats a fixed distance
away from you, simply placed on top of your camera's video feed.

Additionally, in many cases where AR is used, the task could be accomplished as well 
or better without AR~\autocite{theappsolutions2018}. Returning to the Pokemon GO
example, when the AR feature is left on while capturing a Pokemon, the extra power
needed for this feature drains the device faster, makes it harder to hit the Pokemon
with a Pokeball due to the model drifting in the environment, and can even slow app
performance, all of which detract from the ability to play and enjoy the game.

One of the biggest problems facing AR development as a whole, and one that we
ran into as well, is limited hardware. For starters, smartphone cameras present
a major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or barcode
markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on smartphones
can also be too imprecise for good AR tracking~\autocite{geospatialworld2018}.

The biggest hardware limitation comes from which platform to use. AR apps are most
commonly designed for smartphones due to their relatively low cost and how accessible
they are. But, as we just discussed, smartphones come with a host of hardware
limitations that make achieving satisfying AR capabilities difficult. Additionally, AR apps
for smartphones tend not to be very user-friendly, and oftentimes even complicate
the task or activity they were meant to enhance~\autocite{theappsolutions2018}.
The alternative then is to turn to dedicated hardware, like Microsoft's HoloLens. 
But dedicated hardware like the HoloLens is very inaccessible and expensive; 
Microsoft only offers developer editions of the HoloLens, and for the incredibly steep 
price of \$3,500~\autocite{microsoft2019}.

The challenges we faced during development mirrored these that plague the industry
as a whole very accurately. We struggled with how exactly we would us AR for our app
in a way that benefit the experience as a whole, but believe the way we've implemented
it will enhance the user's experience. Hardware issues were definitely our biggest challenge.
Only one of our phones is new enough to run AR technology at a decent level, making
testing of our application difficult.
